---
title: "Introduction Exploratory Data Analysis"
author: George Whittington
date: today
date-format: long
---

# Set Up

```{r}
#| label: libraries
#| output: false

library(tidyverse)
library(here)
library(gt)
```

```{r}
#| label: configure-here
#| output: false

i_am("analysis/analysis_gw.qmd")
```

```{r}
#| label: load-helper-functions

source(here("analysis", "helper.R"))
```

# Source Apportionment

Source apportionment is a "collection of techniques to provide information regarding how much a source (usually a generalized category) contributes to the overall pollutant concentration at receptor (usually a monitoring site)" (Rizzo, 2010).

"Source apportionment is the process of statistically estimating the relative contributions from a set of sources to the observed sample data" (Smith, 2025).

In our case, we will use source apportionment as a method of unsupervised learning applied to air quality data. By analyzing the chemical composition of each observation, we will use Non-Negative/Positive Matrix Factorization (NMF/PMF) to extract latent factors from the data. We can then interpret these factors to identify specific source profiles (the chemical makeup of the source) and calculate their corresponding source contributions (the amount of pollution from that source) over time.

Statistically, this approach functions as a specialized form of Factor Analysis. While traditional Factor Analysis allows for negative values in its mathematical solution, our context requires a strict non-negativity constraint because physical matter (pollution) cannot exist in negative quantities. Therefore, we treat the unknown pollution sources as latent factors (hidden variables that drive the observed variance in the data) and solve for them using algorithms that enforce positive values.

# Datasets

For this project, the EPA has provided six data files:

- Dataset-Baltimore_con.csv
- Dataset-Baltimore_unc.csv

- Dataset-BatonRouge-con.csv
- Dataset-BatonRouge-unc.csv

- Dataset-StLouis-con.csv
- Dataset-StLouis-unc.csv

Where the *_con files represent the readings from the detection device and the *_unc files represent the uncertainty of those readings, or the standard deviation of the readings. This comes into play where we can see how reliable the readings of each chemical were for that day. A flat 10% uncertainty could just be a baseline for that given chemical. But given an uncertainty that is higher than the observed value, that might indicate that the observation fell out of the range of detection for the measurement device. 

## Baltimore

Read in both concentration and uncertainty files

```{r}
#| label: load-baltimore

baltimore_concentration <- read_csv(here("data", "Dataset-Baltimore_con.csv")) |> convert_to_date()
baltimore_uncertainty <- read_csv(here("data", "Dataset-Baltimore_unc.csv")) |> convert_to_date()
```

### Concentration

```{r}
#| label: first-glimpse-baltimore-concentration

glimpse(baltimore_concentration)
```

Here we can see the data type and a top glimpse into the value of each of the columns. Here can see there is one column of dates, and then the concentration of each of the chemical/elements give as a double. 

```{r}
#| label: tbl-head-tail
#| tbl-cap: First and Last 5 Rows

bind_rows(
    baltimore_concentration |> slice_head(n = 5),
    baltimore_concentration |> slice_tail(n = 5)
) |> 
    gt()
```

### Uncertainty

## BatonRouge

Read in both concentration and uncertainty files

```{r}
#| label: load-baton-rouge

baton_rouge_concentration <- read_csv(here("data", "Dataset-BatonRouge-con.csv")) |> convert_to_date()
baton_rouge_uncertainty <- read_csv(here("data", "Dataset-BatonRouge-unc.csv")) |> convert_to_date()
```

## StLouis

Read in both concentration and uncertainty files

```{r}
#| label: load-st-louis

st_louis_concentration <- read_csv(here("data", "Dataset-StLouis-con.csv")) |> convert_to_date()
st_louis_uncertainty <- read_csv(here("data", "Dataset-StLouis-unc.csv")) |> convert_to_date()
```

# Links

## Useful Reference for modeling later

<a href="https://cloud.r-project.org/web/packages/pcpr/vignettes/pcp-applied.html" target="_blank" rel="noopener noreferrer">R code example doing Non-Negative Matrix Factorization</a>

## References

<a href="https://www.nrcs.usda.gov/sites/default/files/2022-10/4-Source-Apportionment.pdf" target="_blank" rel="noopener noreferrer">Powerpoint also on elc. This is Rizzo</a>

