---
title: 'ARIMA Modeling of PCR Residuals: Baltimore, Baton Rouge, St. Louis'
output:
  pdf_document: default
  html_document: default
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 5)
```

# ── 0. Libraries ─────────────────────────────────────────────────────────────

```{r libraries}
library(tidyverse)
library(forecast)    # auto.arima, Acf, Pacf, checkresiduals
library(tseries)     # adf.test, kpss.test
library(lmtest)      # coeftest
library(gridExtra)

library(conflicted)
conflict_prefer("filter",    "dplyr")
conflict_prefer("lag",       "dplyr")
conflict_prefer("select",    "dplyr")
```

# ── 1. Load PCR Residuals ────────────────────────────────────────────────────

```{r load_data}
resid_balt <- read_csv("pcr_residuals_baltimore.csv",   show_col_types = FALSE)
resid_br   <- read_csv("pcr_residuals_baton_rouge.csv", show_col_types = FALSE)
resid_stl  <- read_csv("pcr_residuals_st_louis.csv",    show_col_types = FALSE)

resid_all <- bind_rows(resid_balt, resid_br, resid_stl) %>%
  mutate(date = as.Date(date)) %>%
  arrange(city, date)

cat("Rows per city:\n")
resid_all %>% count(city) %>% print()
```

# ── 2. Detect and Split at Data Gaps ─────────────────────────────────────────
# The handoff notes warn about data gaps. We identify gaps where consecutive
# observations are separated by more than a threshold (e.g., >2× the median
# spacing), then split into contiguous segments.

```{r split_segments}
GAP_MULTIPLIER <- 2  # gap = spacing > GAP_MULTIPLIER × median spacing

split_into_segments <- function(df) {
  df <- df %>% arrange(date)
  diffs       <- as.numeric(diff(df$date))
  med_spacing <- median(diffs, na.rm = TRUE)
  gap_thresh  <- GAP_MULTIPLIER * med_spacing

  gap_idx <- which(diffs > gap_thresh)

  if (length(gap_idx) == 0) {
    df$segment <- 1L
    return(df)
  }

  breaks   <- c(0, gap_idx, nrow(df))
  seg_ids  <- rep(seq_along(diff(breaks)), times = diff(breaks))
  df$segment <- seg_ids
  df
}

resid_segmented <- resid_all %>%
  group_by(city) %>%
  group_modify(~ split_into_segments(.x)) %>%
  ungroup()

seg_summary <- resid_segmented %>%
  group_by(city, segment) %>%
  summarise(
    n          = n(),
    start_date = min(date),
    end_date   = max(date),
    .groups    = "drop"
  )

cat("=== Segment Summary ===\n")
print(seg_summary)
cat("\nSegments with < 30 observations will be skipped for ARIMA fitting.\n")
```

# ── 3. Per-Segment Stationarity & Autocorrelation Tests ──────────────────────

```{r segment_tests}
MIN_OBS <- 30   # minimum segment length for reliable ARIMA

run_segment_tests <- function(df_seg) {
  city <- unique(df_seg$city)
  seg  <- unique(df_seg$segment)
  r    <- df_seg$residual

  if (length(r) < MIN_OBS) {
    cat(sprintf("  [%s | seg %d] n=%d — SKIPPED (< %d obs)\n",
                city, seg, length(r), MIN_OBS))
    return(tibble(
      city = city, segment = seg, n = length(r),
      adf_p = NA, kpss_p = NA, ljung_box_p = NA,
      stationary = NA, autocorrelation = NA, recommended_d = NA_integer_,
      skip = TRUE
    ))
  }

  adf  <- tseries::adf.test(r, alternative = "stationary")
  kpss <- tseries::kpss.test(r, null = "Level")
  lb   <- Box.test(r, lag = min(20, floor(length(r) / 5)), type = "Ljung-Box")

  stat_adf  <- adf$p.value < 0.05
  stat_kpss <- kpss$p.value >= 0.05
  stationary <- stat_adf & stat_kpss

  rec_d <- if (stationary) 0L else 1L

  cat(sprintf("  [%s | seg %d] n=%d | ADF p=%.4f (%s) | KPSS p=%.4f (%s) | LB p=%.4f (%s) | d=%d\n",
              city, seg, length(r),
              adf$p.value,  ifelse(stat_adf,  "stat", "NON-stat"),
              kpss$p.value, ifelse(stat_kpss, "stat", "NON-stat"),
              lb$p.value,   ifelse(lb$p.value < 0.05, "autocorr", "white noise"),
              rec_d))

  tibble(
    city            = city,
    segment         = seg,
    n               = length(r),
    adf_p           = round(adf$p.value,  4),
    kpss_p          = round(kpss$p.value, 4),
    ljung_box_p     = round(lb$p.value,   4),
    stationary      = stationary,
    autocorrelation = lb$p.value < 0.05,
    recommended_d   = rec_d,
    skip            = FALSE
  )
}

cat("=== Per-Segment Stationarity & Autocorrelation ===\n")
seg_tests <- resid_segmented %>%
  group_by(city, segment) %>%
  group_modify(~ run_segment_tests(.x)) %>%
  ungroup()

print(seg_tests)
```

# ══════════════════════════════════════════════════════════════════════════════
# PART I — AUTO.ARIMA FITTING
# ══════════════════════════════════════════════════════════════════════════════

# ── 4. Fit ARIMA per Segment ─────────────────────────────────────────────────

```{r fit_arima}
fit_segment_arima <- function(df_seg, seg_info) {
  city <- unique(df_seg$city)
  seg  <- unique(df_seg$segment)
  r    <- df_seg$residual

  info <- seg_info %>% filter(city == !!city, segment == !!seg)
  if (nrow(info) == 0 || info$skip) return(NULL)

  # Use recommended_d as starting constraint for auto.arima
  rec_d <- info$recommended_d

  # auto.arima with stepwise + approximation for speed,
  # then refit with exact ML if desired
  fit <- tryCatch(
    auto.arima(r,
               d             = rec_d,
               max.p         = 5,
               max.q         = 5,
               max.order     = 10,
               seasonal      = FALSE,   # no seasonality assumed
               stepwise      = TRUE,
               approximation = FALSE,
               ic            = "aicc"),
    error = function(e) {
      cat(sprintf("  [%s | seg %d] auto.arima FAILED: %s\n", city, seg, e$message))
      NULL
    }
  )

  if (is.null(fit)) return(NULL)

  ord <- arimaorder(fit)
  cat(sprintf("  [%s | seg %d] -> ARIMA(%d,%d,%d) | AICc=%.2f | BIC=%.2f\n",
              city, seg, ord[1], ord[2], ord[3], fit$aicc, fit$bic))

  list(
    city    = city,
    segment = seg,
    n       = length(r),
    order   = ord,
    fit     = fit,
    resids  = residuals(fit),
    dates   = df_seg$date
  )
}

arima_fits <- resid_segmented %>%
  group_by(city, segment) %>%
  group_split() %>%
  map(~ fit_segment_arima(.x, seg_tests)) %>%
  compact()   # drop NULLs (skipped segments)

cat(sprintf("\nFitted %d ARIMA models across all city-segments.\n", length(arima_fits)))
```

# ── 5. ARIMA Model Summary Table ─────────────────────────────────────────────

```{r arima_summary_table}
arima_summary <- map_dfr(arima_fits, function(af) {
  ord <- af$order
  fit <- af$fit
  tibble(
    city    = af$city,
    segment = af$segment,
    n       = af$n,
    p       = ord[1],
    d       = ord[2],
    q       = ord[3],
    model   = sprintf("ARIMA(%d,%d,%d)", ord[1], ord[2], ord[3]),
    aicc    = round(fit$aicc, 2),
    bic     = round(fit$bic,  2),
    sigma2  = round(fit$sigma2, 4),
    log_lik = round(fit$loglik, 2)
  )
})

cat("=== ARIMA Model Summary ===\n")
print(arima_summary)
```

# ── 6. Coefficient Tables ────────────────────────────────────────────────────

```{r coef_tables}
for (af in arima_fits) {
  cat(sprintf("\n--- %s | Segment %d | %s ---\n",
              af$city, af$segment,
              sprintf("ARIMA(%d,%d,%d)", af$order[1], af$order[2], af$order[3])))

  if (length(coef(af$fit)) == 0) {
    cat("  (White noise — no coefficients to test)\n")
  } else {
    print(coeftest(af$fit))
  }
}
```

# ══════════════════════════════════════════════════════════════════════════════
# PART II — ARIMA DIAGNOSTICS
# ══════════════════════════════════════════════════════════════════════════════

# ── 7. Ljung-Box on ARIMA Residuals (White Noise Check) ──────────────────────

```{r arima_ljung_box}
arima_diag <- map_dfr(arima_fits, function(af) {
  r   <- residuals(af$fit)
  n   <- length(r)
  lag <- min(20, floor(n / 5))
  lb  <- Box.test(r, lag = lag, type = "Ljung-Box")
  sw  <- if (n >= 5 & n <= 5000) shapiro.test(r) else list(p.value = NA)

  tibble(
    city           = af$city,
    segment        = af$segment,
    model          = sprintf("ARIMA(%d,%d,%d)", af$order[1], af$order[2], af$order[3]),
    lb_lag         = lag,
    lb_p           = round(lb$p.value, 4),
    white_noise    = ifelse(lb$p.value >= 0.05, "YES", "NO - residual autocorrelation"),    shapiro_p      = round(sw$p.value, 4),
    normal_resids  = ifelse(sw$p.value >= 0.05, "YES", "NO (not required for ARIMA)")
  )
})

cat("=== ARIMA Residual Diagnostics ===\n")
print(arima_diag)
```

# ── 8. Diagnostic Plots (ACF, Histogram, Residual Series) ────────────────────

```{r arima_diagnostic_plots, fig.height=6}
for (af in arima_fits) {
  cat(sprintf("\n--- %s | Segment %d ---\n", af$city, af$segment))

  r <- residuals(af$fit)

  p1 <- ggplot(tibble(date = af$dates, residual = as.numeric(r)),
               aes(date, residual)) +
    geom_line(alpha = 0.6) +
    geom_hline(yintercept = 0, linetype = 2, color = "tomato") +
    labs(title = "ARIMA Residuals Over Time", x = "Date", y = "Residual") +
    theme_minimal()

  p2 <- ggplot(tibble(r = as.numeric(r)), aes(r)) +
    geom_histogram(aes(y = after_stat(density)), bins = 30,
                   fill = "steelblue", alpha = 0.6) +
    stat_function(fun = dnorm,
                  args = list(mean = mean(r), sd = sd(r)),
                  color = "tomato", linewidth = 0.8) +
    labs(title = "Residual Distribution", x = "Residual", y = "Density") +
    theme_minimal()

  p3 <- ggplot(tibble(r = as.numeric(r)), aes(sample = r)) +
    stat_qq(alpha = 0.45) + stat_qq_line() +
    labs(title = "Normal Q-Q", x = "Theoretical", y = "Sample") +
    theme_minimal()

  # ACF of ARIMA residuals
  acf_vals <- acf(r, lag.max = 30, plot = FALSE)
  acf_df   <- tibble(lag = acf_vals$lag[-1], acf = acf_vals$acf[-1])
  ci       <- qnorm(0.975) / sqrt(length(r))

  p4 <- ggplot(acf_df, aes(lag, acf)) +
    geom_hline(yintercept = c(-ci, ci), linetype = 2, color = "steelblue") +
    geom_hline(yintercept = 0) +
    geom_segment(aes(xend = lag, yend = 0)) +
    labs(title = "ACF of ARIMA Residuals", x = "Lag", y = "ACF") +
    theme_minimal()

  title_str <- sprintf("%s | Seg %d | ARIMA(%d,%d,%d)",
                       af$city, af$segment,
                       af$order[1], af$order[2], af$order[3])

  print(grid.arrange(p1, p2, p3, p4, ncol = 2, top = title_str))
}
```

# ══════════════════════════════════════════════════════════════════════════════
# PART III — FORECASTING & RECONSTRUCTION
# ══════════════════════════════════════════════════════════════════════════════

# ── 9. Forecast ARIMA Residuals (h-step ahead) ──────────────────────────────

```{r forecast_arima, fig.height=4}
H_STEPS <- 30   # forecast horizon (number of future time steps)

forecasts <- map(arima_fits, function(af) {
  fc <- forecast(af$fit, h = H_STEPS, level = c(80, 95))

  title_str <- sprintf("%s | Seg %d | ARIMA(%d,%d,%d) — %d-step Forecast",
                       af$city, af$segment,
                       af$order[1], af$order[2], af$order[3], H_STEPS)

  print(autoplot(fc) +
    labs(title = title_str, x = "Index", y = "Residual Forecast") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5)))

  list(city = af$city, segment = af$segment, forecast = fc)
})
```

# ── 10. Reconstruct Predicted y = OLS Fitted + ARIMA Forecast ────────────────
# This shows how to combine PCR fitted values with ARIMA residual forecasts
# to get final predictions. For in-sample, we add ARIMA fitted residuals back
# to the OLS fitted values.

```{r reconstruct, fig.height=4}
for (af in arima_fits) {
  city <- af$city
  seg  <- af$segment

  # Get the original residual data for this segment
  seg_data <- resid_segmented %>%
    filter(city == !!city, segment == !!seg)

  # In-sample reconstruction: y_hat_final = OLS_fitted + ARIMA_fitted_residual
  arima_fitted_resid <- af$fit$fitted   # ARIMA's in-sample fitted values of the residual
  # Note: the original OLS residual = y - OLS_fitted
  # ARIMA models that residual, so:
  # y_hat_combined = OLS_fitted + ARIMA_fitted(residual)

  recon <- seg_data %>%
    mutate(
      arima_fitted_resid = as.numeric(arima_fitted_resid),
      y_hat_combined     = fitted + arima_fitted_resid
    )

  rmse_ols      <- sqrt(mean((recon$y - recon$fitted)^2))
  rmse_combined <- sqrt(mean((recon$y - recon$y_hat_combined)^2))

  cat(sprintf("\n%s | Seg %d | OLS RMSE = %.4f | OLS+ARIMA RMSE = %.4f | Improvement = %.1f%%\n",
              city, seg, rmse_ols, rmse_combined,
              (1 - rmse_combined / rmse_ols) * 100))

  p <- recon %>%
    select(date, Observed = y, `OLS Only` = fitted, `OLS + ARIMA` = y_hat_combined) %>%
    pivot_longer(-date, names_to = "Series", values_to = "value") %>%
    ggplot(aes(date, value, color = Series)) +
    geom_line(alpha = 0.7) +
    scale_color_manual(values = c("Observed" = "black",
                                  "OLS Only" = "gray60",
                                  "OLS + ARIMA" = "steelblue")) +
    labs(
      title    = sprintf("%s | Seg %d: Observed vs Fitted", city, seg),
      subtitle = sprintf("OLS RMSE=%.3f → OLS+ARIMA RMSE=%.3f (%.1f%% improvement)",
                         rmse_ols, rmse_combined,
                         (1 - rmse_combined / rmse_ols) * 100),
      x = "Date", y = seg_data$city[1] %>%
        { if (. == "Baton Rouge") "TNMOC" else "PM2.5" }
    ) +
    theme_minimal(base_size = 11) +
    theme(plot.title    = element_text(face = "bold", hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, color = "gray40"),
          legend.position = "bottom")

  print(p)
}
```

# ── 11. Final Summary & Export ────────────────────────────────────────────────

```{r final_export}
# Combine everything
final_summary <- arima_summary %>%
  left_join(arima_diag %>% select(city, segment, lb_p, white_noise, shapiro_p),
            by = c("city", "segment"))

cat("=== Final ARIMA Summary ===\n")
print(final_summary)

write_csv(arima_summary, "arima_model_summary.csv")
write_csv(arima_diag,    "arima_diagnostics.csv")

# Export per-segment fitted values for reconstruction
for (af in arima_fits) {
  seg_data <- resid_segmented %>%
    filter(city == af$city, segment == af$segment)

  export_df <- seg_data %>%
    mutate(
      arima_fitted_resid = as.numeric(af$fit$fitted),
      y_hat_combined     = fitted + arima_fitted_resid,
      arima_residual     = as.numeric(residuals(af$fit))
    )

  fname <- sprintf("arima_fitted_%s_seg%d.csv",
                   tolower(gsub(" ", "_", af$city)), af$segment)
  write_csv(export_df, fname)
  cat("  Saved:", fname, "\n")
}

cat("\nAlso saved:\n")
cat("  arima_model_summary.csv\n")
cat("  arima_diagnostics.csv\n")
```
